% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}
This work contains the outcomes of prolonged research endeavours which would not have been accomplished without my interaction with many outstanding collegues. I express my deep gratitude to my supervisor, Cecilia Mascolo, for generously granting me vast stretches of freedom to pursue my own research direction, her unabated trust in my work, and her encouragement and advice over the ups and downs of my PhD. I'm also grateful to \mbox{Trevor Campbell} for his bold and intellectually stimulating collaboration: my perspective on science has been crucially enriched by his adherence to first principles and his enthusiasm on research. My close collaboration with Alastair Beresford was most valuable over the time I started delving into the subject of data privacy---also, \mbox{Borja Balle's} teaching on differential privacy has been instrumental in unveiling the wonders and beauty of the field. I'm indebted to my labmates at the Mobile Systems Group, Nokia Bell Labs, Max Planck Institute, and the rest of my collaborators: Shubham Aggarwal, Sourav Bhattacharya, Alberto Jes\'{u}s Coca, Abir De, Manuel Gomez Rodriguez, Fahim Kawsar, Nic Lane,  Akhil Mathur, Chulhong Min, Alberto Gil Ramos, and \mbox{Rik Sarkar}. My warm thanks to \mbox{Michael Schaub} and Kostas Kyriakopoulos: their mentorship over my first awkward steps in academic inquiry, provided me with solid foundations which were substantial over my PhD. Thanks to Mattias Grossglauser and \mbox{Amanda Prorok} for serving as members of my thesis committee.

I gratefully acknowledge the financial support received from Nokia Bell Labs, Lundgren Fund, Darwin College Cambridge, and the Department of Computer Science \& Technology that backed my research. 

Writings of Sebald, Bola{\~{n}}o, Benjamin, Parra, Herbert, activities at Darwin College Film Club, and university Canoeing and Tango societies kept me reinvigorating company over rest breaks. Antonis, Jenny and Panos made my time enjoyable supporting me with their friendship at all times---Pano, your light-spirited theory on information overflow has been a paradoxical source of inspiration over my research on coresets. Finally, my deepest thanks to Mum, Dad, Lena and Memos for keeping a shelter of unwavering love and support alive through all my successes and failures.
\end{acknowledgements}
